\documentclass{article}
\usepackage{fontspec}
\usepackage{multicol}
\usepackage{enumitem}
\usepackage[paperheight=7in,paperwidth=5in,margin=0.3in,heightrounded]{geometry}

\setlength{\parindent}{0in}
\setlength{\parskip}{8pt}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

\setmainfont{Futura Std}

\begin{document}

% \fontspec{Futura Std}
% \fontsize{9}{13.9}
% \selectfont
\fontsize{10}{10}\selectfont

\textbf{Thank you for buying X1Plus Expander!}  Included in this box, you will find:

\fontsize{9}{9}\selectfont
\begin{multicols}{2}
\begin{itemize}
\item{This document.}
\vspace{-3pt}
\item{1x X1P-001 wiring harness.}
\vspace{-3pt}
\item{1x X1P-002 mainboard.}
\vspace{-3pt}
\item{3x M3 x 12mm screws.}
\vspace{-3pt}
\item{1x M3 x 18mm screw.}
\vspace{-3pt}
\item{1x ping-pong ball.}
\vspace{-3pt}
\end{itemize}
\end{multicols}
\fontsize{10}{10}\selectfont

\vspace{-8pt}

First, take a moment to make sure you have it all (especially the ping-pong
ball, which Peanut, the cat, told me was very important to include), and
have a read through the Instructions for Safe Use below (or, if you prefer,
\textit{auf Deutsch} on the other side).  Then, scan the QR
code on the box, or go to https://accelerated.tech/expander/, to get started
installing your Expander into your printer.

\hspace*{3in}Happy printing! \\
\hspace*{3in}joshua (and Peanut)

\begin{center}
\fontsize{14}{14}\selectfont
\textbf{Instructions for Safe Use}
\end{center}

\fontsize{8}{8}\selectfont
Expander is not designed for safety-critical applications, like closed loop
control of a chamber heater.  Safety-critical applications must have
failsafes independent of the Expander hardware.

Modifying 3D printers with
community-provided firmware carries inherent risk.  Modified or not, always
supervise your printer when it is in operation.

Do not draw more than 2A at
5V, or 1A at 3.3V, or a total of 10W, from Expander’s built in power
supplies.  Limit current through each pin to the amount specified by each
connector.

Expander must be connected only to the power supply built into the
X1 Carbon.

Expander should be covered by a non-conductive case, and must not
be contacted by conductive items.

The connection of unapproved devices to any
receptacle may affect compliance or result in damage to the unit and
invalidate the warranty.

Do not expose Expander to water, moisture, or place
it on a conductive surface while it is in operation.  Do not place it inside
the printer’s print area, and keep it away from heat.

Take care when handling to avoid mechanical or electrical damage to the
printed circuit board and connectors.  Avoid handling Expander while it is
powered.  Handle Expander only by the edges to minimize the risk of
electrostatic discharge damage.

All peripherals used with Expander should comply with relevant
standards for the country of use and be marked accordingly to ensure that
safety and performance requirements are met.  These articles include but are
not limited to the add-on modules used in conjunction with Expander.

\enddocument
